CamIO data analysis

### 2020-06-09 R/01-visualizations.Rmd
Update figures

```{r warnings=F}
desc <- data.long %>%
  group_by(mode) %>%
  summarize(
    n = n(),
    median = median(time),
    mean = mean(time),
    sd = sd(time),
    skew = skewness(time),
    kurt = kurtosis(time),
    SW.p = shapiro.test(time)$p.value
  )

DT::datatable(
  desc,
  class = 'cell-border stripe compact',
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Summary statistics'))
) %>% 
  formatRound(5:ncol(desc), 4) %>%
  formatStyle(
    'SW.p',
    color = styleInterval(alpha, c('red', 'gray')),
    fontWeight = styleInterval(alpha, c('bold', 'normal')),
  )
```

@@

```{r}
fig <- data.long %>% 
  group_by(mode) %>% 
  mutate(med = median(time)) %>% 
  ungroup() %>%
  ggplot(aes(x=time, fill=mode, color=mode)) +
  geom_histogram(aes(y=..density..), binwidth=15, alpha=0.8, fill="white", boundary = 1) +
  geom_density(alpha=0.6, adjust=6) + 
  theme(legend.position = "none") +
  labs(title= glue('Fig {tc<-tc+1}: Score distributions + median values per type of guidance'), x = "Time to find hotspot") +
  facet_wrap(. ~ mode) +
  geom_vline(aes(xintercept=med, group=mode, color=mode), linetype="dashed", size=1) +
  geom_text(aes(x=med - 10, label=med, y=0.055))

@@

fig <- dat %>%
  ggplot(aes(x = mode, y = time, color = subject)) + #group=1
  geom_line(position = pd) +
  geom_errorbar(aes(ymin = time - se, ymax = time + se), width = .1, position = pd) +
  geom_point(shape=21, size=2, fill="white", position = pd)

>>>>

```{r warnings=F}
library(pillar)
options(pillar.sigfig=3)

desc <- data.long %>%
  group_by(mode) %>%
  summarize(
    n = n(),
    median = median(time),
    mean = mean(time),
    sd = sd(time),
    skew = skewness(time),
    kurt = kurtosis(time),
    SW.p = shapiro.test(time)$p.value
  ) %>% mutate(across(where(is.character), as.numeric))

td <- tabl(desc)

DT::datatable(
  desc,
  class = 'cell-border stripe compact',
  caption = htmltools::tags$caption(
    style = 'caption-side: bottom; text-align: center;',
    glue('Fig {tc<-tc+1}: Summary statistics'))
) %>% 
  formatRound(4:ncol(desc)-1, 2) %>%
  formatRound(ncol(desc), 4)
  # formatStyle(
  #   'SW.p',
  #   color = styleInterval(alpha, c('red', 'gray')),
  #   fontWeight = styleInterval(alpha, c('bold', 'normal')),
  # )

# png("../res/img/tab1.png", width=480, height=480, bg = "white")
# grid.table(desc)
# dev.off()
```

@@

```{r}
fig <- data.long %>% 
  group_by(mode) %>% 
  mutate(med = median(time)) %>% 
  ungroup() %>%
  ggplot(aes(x=time, fill=mode, color=mode)) +
  geom_histogram(binwidth=12, fill="white", boundary = 1) + #aes(y=..density..)
  geom_density(alpha=0.6, adjust=6) + 
  theme(legend.position = "none") +
  labs(x = "Time to find hotspot", y="Count") +
  facet_wrap(. ~ mode) +
  geom_vline(aes(xintercept=med, group=mode, color=mode), linetype="dashed", size=1) +
  geom_text(aes(x=med - 10, label=med, y=-1.5))

ggsave(plot=fig, filename="../res/img/histNG.png", device="png", dpi=320, scale=1)
ggplotly(fig)
```

@@

fig <- dat %>%
  ggplot(aes(x = mode, y = time, color = subject)) + #group=1
  geom_line(position = pd) +
  geom_errorbar(aes(ymin = time - se, ymax = time + se), width = .1, position = pd) +
  geom_point(shape=21, size=2, fill="white", position = pd) +
  labs(x="Guidance mode", y="Time to find hotspot")

ggplotly(fig)
ggsave(plot=fig, filename="../res/img/lines.png", device="png", dpi=320, scale=1)
```

### 2020-06-09 R/Index.Rmd
Update figures

```{r setup, include=FALSE, cache=FALSE}

if (!require(pacman)) install.packages("pacman")

pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast")

pacman::p_load(char = pkg_list) #update=TRUE
pacman::p_load_gh(c("rstudio/gt", "tidyverse/dplyr"))
#knitr::write_bib(c(.packages(), pkg_list), 'bib/packages.bib')

@@

options(scipen=999, digits=5)

@@

initial.data <- "../data/initial.csv"
```

```{r}
sessionInfo()

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("layout", "plotly")

# includes:
#   in_header: header.html
#   after_body: sig.html
```

>>>>

```{r include=FALSE}

if (!require(knitr)) install.packages("knitr")
if (!require(pacman)) install.packages("pacman")
pkg_list <- c("tidyverse", "glue", "broom", "magrittr", "prettydoc", "DT", "reshape2", "plotly", "moments", "emmeans", "gtsummary", "lmtest", "table1", "rstatix", "lme4", "ggeffects", "conflicted", "forecast", "Rmisc", "gridExtra", "kableExtra", "magick", "webshot")

pacman::p_load(char = pkg_list) #update=TRUE
#pacman::p_load_gh(c("rstudio/gt", "tidyverse/dplyr"))
#knitr::write_bib(c(.packages(), pkg_list), 'bib/packages.bib')

@@

options(scipen=999, digits=4)

@@

initial.data <- "../data/initial.csv"

conflict_prefer("mutate", "dplyr")
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("summarize", "dplyr")
conflict_prefer("layout", "plotly")

tabl <- function(data, title="Table caption") {
  kable(data, col.names=gsub("[.]", " ", names(data)), booktabs=T, align="c", digits=3, format.args=list(big.mark=",", scientific=FALSE), escape=F, caption=title, linesep=c("")) %>% 
    kable_styling(font_size = 10, latex_options = c("striped", "scale_down", "hold_position"), position = "left") %>%
    row_spec(0, background = "#d4dbde", bold = T, color = "#2b4894")
}
options(knitr.table.format = ifelse(knitr::is_latex_output(), "latex", "pandoc"), knitr.kable.NA = "")
```

```{r}
sessionInfo()
```
